---
title: "RWorksheet#6"
author: "Ann Margaret Camayodo BSIT 2-C"
date: "2023-12-111"
output: pdf_document
---
```{r}
install.packages("Hmisc")
install.packages("pastecs")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(Hmisc)
library(pastecs)
test <- data.frame(
  Student = c(1,2,3,4,5,6,7,8,9,10),
  PreTest = c(55,54,47,57,51,61,57,54,63,58),
  PostTest = c(61,60,56,63,56,63,59,56,62,61)
)
summary_hmisc <- describe(test)

summary_pastecs <- stat.desc(test)

cat("Descriptive Statistics using Hmisc:\n")
print(summary_hmisc)

print(summary_pastecs)

```
#2. The Department of Agriculture was studying the effects of several levels of a fertilizer on the growth of a plant. For some analyses, it might be useful to convert the fertilizer levels to an ordered factor.
```{r}
data <- c(10, 10, 10, 20, 20, 50, 10, 20, 10, 50, 20, 50, 20, 10)
factor_data <- factor(data, levels = c(10, 20, 50), ordered = TRUE)

```
#3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study the exercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” , “l”, “n”,“n”, “i”, “l” ; n=none, l=light, i=intense
a. What is the best way to represent this in R?
```{r}
exercise_levels <- c("l", "n", "n", "i", "l", "l", "n", "n", "i", "l")

```
#4. Sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics as:
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
"vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
"wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
"vic", "vic", "act")
a. Apply the factor function and factor level. Describe the results.
```{r}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
           "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
           "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
           "vic", "vic", "act")

state_factor <- factor(state)
```
#4From #4 - continuation:
• Suppose we have the incomes of the same tax accountants in another vector (in suitably
large units of money)
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
a. Calculate the sample mean income for each state we can now use the special function
tapply():
Example: giving a means vector with the components labelled by the levels
incmeans <- tapply(incomes, statef, mean)
Note: The function tapply() is used to apply a function, here mean(), to each group
of components of the first argument, here incomes, defined by the levels of the second
component, here state 2
• 2
that tapply() also works in this case when its second argument is not a factor,
• e.g., ‘tapply(incomes, state)’, and this is true for quite a few other functions, since
arguments are coerced to factors when necessary (using as.factor()).

b. Copy the results and interpret.
```{r}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)

incmeans <- tapply(incomes, state_factor, mean)

```